Pop-up cycleways and pedestrian spaces: a peak into post Covid-19 transport futures

### 2020-05-11 conversation.Rmd

In the coming weeks and months, active travel will play a vital role in enabling the reopening of many countries. As travel increases, we must ensure that safe, socially distanced walking and cycling remains possible. Maintaining social distancing on public transport could severely reduce the capacity of rail and bus networks, and there is a risk that this may lead to a rapid rise in road traffic. Without careful management, increased congestion could deter others from the streets, especially as [ record bicycle sales ] suggest that many people have taken advantage of lockdown conditions to take up or return to cycling. Some of these cyclists may have less confidence in dealing with high volumes of road traffic.

@@

These measures can all be undertaken on a temporary basis, but if action is prioritised in places where there is a *long-term need* for cycle improvements, there is a greater chance that people will demand they become permanent. This is what happened with the experimental cycleway in Torrington Place in London, where a 2 way road for motor vehicles has been converted into a thriving 2 way cycleway, enabling social distancing and zero emissions transport for keyworkers in central London. [Paris plans].

@@

The methods have focused on road capacity and cycling potential, identifying roads where a ‘spare lane’ could be re-purposed for cycling. Cycle potential is assessed based on travel to work data and cycling uptake scenarios under the UK Government’s national target of doubling cycling levels by 2025, with the length of road segments also being used to filter the top schemes.

>>>>

Active travel is already [recommended by the World Health Organisation](https://who.canto.global/pdfviewer/viewer/viewer.html?share=share%2Calbum%2CU6GDM&column=document&id=q3v02qdsh114763ffe3apo4s2p&suffix=pdf) as a safe mode of transport, and in the coming weeks and months it will play a vital role in enabling the reopening of many countries. As travel increases, we must ensure that safe, socially distanced walking and cycling remains possible. Maintaining social distancing on public transport could severely reduce the capacity of rail and bus networks, and there is a risk that this may lead to a rapid rise in road traffic.  [ record bicycle sales ] suggest that many people have taken advantage of lockdown conditions to take up or return to cycling, but without careful management, increased traffic congestion could again deter many would-be cyclists from the streets.

@@

These measures can all be undertaken on a temporary basis, but if action is prioritised in places where there is a *long-term need* for cycle improvements, there is a greater chance that people will demand they become permanent. This is what happened with the experimental cycleway in Torrington Place in London, where a 2 way road for motor vehicles has been converted into a thriving 2 way cycleway, enabling social distancing and zero emissions transport for keyworkers in central London. In Paris, measures aim to contribute towards Mayor Anne Hidalgo's long-term [Plan Velo](https://www.curbed.com/2020/1/15/21065343/bike-paris-cycling-anne-hidalgo).

@@

The methods have focused on road capacity and cycling potential, identifying roads where a ‘spare lane’ could be re-purposed for cycling. Cycle potential is assessed based on census data for travel to work and cycling uptake scenarios under the UK Government’s national target of doubling cycling levels by 2025. The length of road segments is also used to filter the top schemes.
